---
title: "Kate's Free Week at Camp: DataCamp, Introduction to Mapping"
output: html_notebook
---


# Table of Contents
1. Introduction
2. Filter Verb
3. placeholder vectors & matrices
4. placeholder Operators
5. placeholder the result: !
6. placeholder Statements
7. placeholder Loop
8. placeholder Loop
9. placeholder 
10. placeholder Your own  Function
11. R placeholder
12. placeholder Apply lapply
13. placeholder
14. placeholder
15. placeholder Functions
16. placeholder Expressions 
17. placeholder Time Objects



# 1. Grabbing a background map
There are two steps to adding a map to a ggplot2 plot with ggmap:

Download a map using get_map()
Display the map using ggmap()
As an example, let's grab a map for New York City:

```{r}
library(ggmap)

nyc <- c(lon = -74.0059, lat = 40.7128)
nyc_map <- get_map(location = nyc, zoom = 10)
```

example: 
```{r}
library(ggmap)
corvallis <- c(lon = -123.2620, lat = 44.5646)

# Get map at zoom level 5: map_5
map_5 <- get_map(corvallis, zoom = 5, scale = 1)

# Plot map at zoom level 5
ggmap(map_5)

# Get map at zoom level 13: corvallis_map
corvallis_map <- get_map(corvallis, zoom = 13, scale = 1)

# Plot map at zoom level 13
ggmap(corvallis_map)
```

solution/ console:
```{r}
# > library(ggmap)
# > corvallis <- c(lon = -123.2620, lat = 44.5646)
# > 
# > # Get map at zoom level 5: map_5
# > map_5 <- get_map(corvallis, zoom = 5, scale = 1)
# > 
# > # Plot map at zoom level 5
# > ggmap(map_5)
# > 
# > # Get map at zoom level 13: corvallis_map
# > corvallis_map <- get_map(corvallis, zoom = 13, scale = 1)
# > 
# > # Plot map at zoom level 13
# > ggmap(corvallis_map)
> 
```


